%-------------------------
% Resume in Latex
% Author : Ryo Wijaya (Updated using provided template)
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ryo Wijaya} \\ \vspace{2pt}
    \small Singapore Citizen $|$ +65 8449 9902 $|$ \href{mailto:mainryo@gmail.com}{\underline{mainryo@gmail.com}} \\
    \vspace{2pt}
    \small 
    \textbf{LinkedIn:} \href{https://linkedin.com/in/ryowijaya}{\underline{linkedin.com/in/ryowijaya}} $|$ 
    \textbf{GitHub:} \href{https://github.com/ryo-wijaya}{\underline{github.com/ryo-wijaya}} $|$ 
    \textbf{Blog:} \href{https://blog.ryo-wijaya.me}{\underline{blog.ryo-wijaya.me}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore $|$ \textnormal{Singapore}}{Aug. 2020 -- June 2024}
      {Bachelor of Computing, Information Systems (Hons. w/ Distinction) $|$ \textit{FinTech Specialisation}}{}
    \resumeSubheading
      {Heidelberg International School $|$ \textnormal{Germany}}{Aug. 2016 -- May 2018}
      {High School Diploma, International Baccalaureate (IB)}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeProjectHeading
      {\textbf{Software Engineer} $|$ \textnormal{Crédit Agricole Corporate \& Investment Bank}}{July 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Contributed to the design and development of a \textbf{greenfield project} to build modular \textbf{ETL Treatment Chains} using \textbf{Spark Streaming}, \textbf{Spring Boot}, and \textbf{GCP}; developed cloud-enabled Java \textbf{drivers} to ingest, enrich, and distribute Commercial Real Estate Loans and Capital Markets data.}
        \resumeItem{Developed an internal \textbf{Spring Boot} platform for automated \textbf{JSON $\leftrightarrow$ Avro} conversion, \textbf{Kafka} topic management, \textbf{PostgreSQL} configuration validation and loading, and \textbf{Apache Iceberg DDL} generation; adopted by cross-functional teams in Singapore and Paris.}
        \resumeItem{Architected and implemented \textbf{OpenID Connect (OIDC) and OAuth2 SSO} authentication for the \textbf{Angular} application platform and developed UI features.}
        \resumeItem{Implemented schema validation across upstream sources and downstream destinations by utilizing \textbf{Confluent Schema Registry} and \textbf{Kafka}. Managed schema evolution across Avro schema version upgrades.}
        \resumeItem{Orchestrated deployments using \textbf{Helm}, \textbf{Kubernetes}, and created \textbf{GitLab CI} pipelines to ensure robust CI/CD.}
        \resumeItem{Contributed to application security by remediating \textbf{Checkmarx} and \textbf{JFrog Xray} vulnerabilities, and enforcing \textbf{SonarQube} quality gates.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{Software Engineer Intern} $|$ \textnormal{SP Group}}{Jan. 2023 -- June 2023}
      \resumeItemListStart
        \resumeItem{Developed an \textbf{OCPP 1.6/2.0.1} compliant electric vehicle charger simulator using \textbf{FastAPI} and \textbf{WebSockets}.}
        \resumeItem{Led load testing for over \textbf{2,000 simulated chargers} to identify infrastructure scalability bottlenecks.}
        \resumeItem{Built a \textbf{Next.js} platform for real-time charger configuration, message triggering, and log monitoring.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Software Engineer Intern} $|$ \textnormal{Reluvate Technologies}}{May 2022 -- Aug. 2022}
      \resumeItemListStart
        \resumeItem{Developed a hiring web platform using \textbf{Node} and \textbf{GCP Cloud Services} to automate over \textbf{90\%} of company recruitment processes, including document exchange and technical assessments.}
        \resumeItem{Built a \textbf{Python} backend for an accounting platform product to handle payments and contracts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Software Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/IS4103-PetHub/PetHub-FE}{\textbf{PetHub}} $|$ \emph{Express.js, Next.js, PostgreSQL, Prisma, AWS}}{}
          \resumeItemListStart
            \resumeItem{E-commerce marketplace for pet-service providers and owners. Facilitates bookings, purchases, and admin management.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\href{https://github.com/ryo-wijaya/Optimal-Travel-Plan}{\textbf{Optimal Travel Plan}} $|$ \emph{Jakarta EE, JSF, MySQL, Ionic}}{}
          \resumeItemListStart
            \resumeItem{Web and hybrid mobile app that generates optimized travel itineraries based on available events/services.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Other Projects}}{}
          \resumeItemListStart
            \resumeItem{\href{https://github.com/ryo-wijaya/ibkr-tv-tradebot}{\textbf{ibkr-tv-tradebot}}: FastAPI server utilizing the \textbf{IBKR TWS API} for order execution and \textbf{TradingView} integration.}
            \resumeItem{\href{https://github.com/ryo-wijaya/my-pi-board}{\textbf{my-pi-board}}: Next.js application for bus timings and stock market monitoring that lives on my Raspberry Pi.}
            \resumeItem{\href{https://blog.ryo-wijaya.me}{\textbf{blog}}: Personal blog utilizing Jekyll and \textbf{GitHub Actions} for automated CI/CD deployment.}
            \resumeItem{\textbf{RAG System}: FastAPI application using \textbf{LangGraph} and \textbf{Qdrant} to implement hybrid (vector + BM25) search.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript/TypeScript, HTML/XHTML, SQL} \\
     \textbf{Technologies}{: Spring Boot, Apache Kafka (Confluent), Apache Spark, Apache Iceberg, FastAPI, Next.js, React.js, Node.js, Angular, PostgreSQL, NoSQL Databases, Liquibase, JEE/JSF, OCPP} \\
     \textbf{Infrastructure \& Tools}{: Kubernetes, Helm, Docker, GitLab CI/CD, Git, Google Cloud Platform (Cloud Run, Artifact Registry, GKE, Compute Engine, Cloud Storage, Cloud SQL, etc), Azure (VM, AKS, Functions, Cosmos DB, Storage, etc)} \\
     \textbf{AI Engineering}{: RAG, LangGraph, LangChain, Qdrant, Ollama} \\
     \textbf{Interests}{: Electric Guitar, Piano, Drums, Music Production} \\
     \textbf{Communication}{: English (Native), German (Conversational), Mandarin (Conversational)}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/11eb9f8b-d2de-46e0-82b0-4a2704349423-ryo-armando-wijaya-778fb699-4b16-4c9f-9c14-6e3d1fc78e51-certificate.pdf}{\textbf{Certified Kubernetes Application Developer (CKAD) - 98/100}} $|$ \emph{CNCF}}{2025}
      \resumeProjectHeading
          {\href{https://certificates.confluent.io/a29862ce-da30-4aba-b353-b97b38259964}{\textbf{Confluent Apache Kafka Fundamentals Accreditation}} $|$ \emph{Confluent}}{2026}
      \resumeProjectHeading
          {\href{https://credentials.nus.edu.sg/b00bb0ae-8419-4336-b33e-afb88d5cc582}{\textbf{Financial Technology Specialisation (Distinction)}} $|$ \emph{National University of Singapore}}{2024}
      \resumeProjectHeading
          {\href{https://credentials.nus.edu.sg/af73a852-f403-4262-ba54-cb15b6a68ccd}{\textbf{IS Technology Knowledge Area (Distinction)}} $|$ \emph{National University of Singapore}}{2024}
    \resumeSubHeadingListEnd

\end{document}